Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-10-24 latex/paper.tex
[UPDATE] Final version for proceeding.

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\HL}[1]{\hl{#1}}
\newcommand{\TG}[1]{\color{red}\textsc{From Tristan: }#1\color{black}}

\articletype{WORKS19 Special Issue on Workflows in Support of Large-Scale Science GEs:  Chase Wu, Hoang Nguyen}

@@

\section*{Acknowledgment}
Mathieu Dugr\'e was funded by the Alexander Graham Bell scholarship from
the Natural Sciences and Engineering Research Council of Canada.
The Canada Research Chairs program partially funded this work.
The Canada Foundation for Innovation funded the HPC cluster.

>>>>

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\HL}[1]{#1}
\newcommand{\TG}[1]{\color{red}\textsc{From Tristan: }#1\color{black}}

\articletype{WORKS19 Special Issue on Workflows in Support of Large-Scale Science GEs:  David Walker, Chase Wu}

@@

\section*{Acknowledgment}
Mathieu Dugr\'e was partially funded by a Alexander Graham Bell scholarship from the Natural
Sciences and Engineering Research Council of Canada and a Master's (B1X) Research Scholarships.
The Canada Research Chairs program partially funded this work.
The Canada Foundation for Innovation funded the HPC cluster.

\section*{Data Availability}
\subsection*{BigBrain}
The data that support the findings of this study are available from the corresponding author, M. Dugr\'e, upon reasonable request.
A lower resolution of \SI{40}{\micro\metre} is available publicly by FTP at: 
\newline\href{https://ftp.bigbrainproject.org/bigbrain-ftp/BigBrainRelease.2015/3D_Blocks/40um/nii/}{https://ftp.bigbrainproject.org/bigbrain-ftp/BigBrainRelease.2015/3D\_Blocks/40um/nii}

\subsection*{CoRR}
The data that support the findings of this study are openly available in DataLad at:
\newline\href{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}

\subsection*{Code}
The code that support the findings of this study is openly available in GitHub at:
\newline\href{https://github.com/big-data-lab-team/paper-big-data-engines/tree/CPE}{https://github.com/big-data-lab-team/paper-big-data-engines/tree/CPE}

\section*{Conflict of Interests}
The authors declare no conflict of interests.
